\documentclass[a4paper,twocolumn]{article}

\usepackage[compact]{titlesec}
\usepackage{enumitem}

\setlist{nosep}

\title{1817 notes}
\author{Xeryus Stokkel}

\begin{document}

\maketitle

\section{Rules}
\begin{itemize}
	\item Loans can be taken whenever a company wants.
	\item Private companies never close (but can be removed if they are not useful any more).
	\item Companies can stay 2-share of 5-share throughout the entire game.
	\item You never have to close shorts.
	\item Can close stock at the share limit.
	\item Cities upgraded to brown should have as many legs as possible.
	\item \textbf{Paying half dividends has to be rounded to a multiple of \$10
		for 10-share companies only. Rounding is in favor of shareholders, so
		round up for the part that is paid as divident.}
	\item When merging two 2-share companies the shares are exchanged 2 for 1.
	So after the merge only 40\% is in the hands of players.
	\item Post conversion/merge players may only buy shares from the treasury.
	Players may also sell, but not short, shares in the company. The president
	may only buy shares, but he may buy as many as he wants.
	\item Shares in the treasury are sold after a friendly sale has taken
	place. \emph{It is not part of the amount that can be bid [7.2.4 step 6]}.
	For liquidation and hostile sale they do not pay cash to the company.
	\item Hostile acquisition has a minimum bid of \$10. Friendly acquisition
	has a minimum bid of market value.
	\item After liquidation shareholders/shorts only have to exchange money if
	there is any money left after the loans have been paid off.
	\item \emph{When companies merge and together they have more than eight
		station tokens then the president can determine per hex whether to keep
		it. Those who he does not wish to keep return to the company charter.
		There may still only be a total of eight markers in play. [7.3]}
	\item During cash crisis a player may not sell shares that would cause him
	to loose presidency.
\end{itemize}

\section{Strategy}
\begin{itemize}
	\item Je kan een company beginnen en niet voor de station tokens betalen.
	De company gaat dan automatisch in liquidatie. Je kan dan een andere
	company gebruiken om de nieuwe company op te kopen en super veel geld naar
	je eigen hand verplaatsen. Het kost hooguit een klein beetje geld als er
	geen leningen in de company zitten, want alle cash in de company satisfies
	de conditie dat er surplus money moet zijn (stap 9 acquisitions).
	\item Company met shares in treasury overnemen zodat de overnemende company
	een cash infusion krijgt door de verkoop van die shares (alleen friendly
	acquisition).
\end{itemize}

\end{document}